Formulating Regional Typologies

### 2023-11-01 regional_typologies.qmd
publish

::: {style="font-size:20px"}
| Criteria                  | Regional Typologies                                                                                 | Regional Indexes                                                                          |
|------------------|------------------------------|------------------------|
| **What it is**            | Categorises areas based on similar socio-economic, environmental, or institutional characteristics. | A single, composite measure that quantifies the level of vulnerability to a threat.       |
| **Outcome**               | Classifications like "urban area" or "rural area."                                                  | Numerical score ranking areas from low to high vulnerability.                             |
| **Use-case**              | Tailoring policies or interventions to different types of areas.                                    | Prioritising aid, resources, or interventions based on the ranking                        |
| **Caveats**               | Can oversimplify complexities; subject to analyst bias.                                             | May not capture the full situation; choice of indicators and weightings can be arbitrary. |
| **Complementary aspects** | Provides rich, contextual information.                                                              | Pinpoints areas needing immediate attention.                                              |

@@

|----------------|----------------|-----------------|------------------------|

@@

| **Typology** | **R.3.1 Establishment of Peatland Stewardship Village**                                                                                                                                                                                                               | **R.3.2 Enhancing Livelihood Capacity**                                                                                                          | **R.3.3 Development of Alternative Commodities and Livelihood Sources**                                                             |
|----------------|----------------|----------------|------------------------|
| **1**        | \- Community awareness about the importance of the peat ecosystem, collaborating with district and provincial governments. <br><br> - Activities of the Peatland Stewardship Village aimed at increasing income and creating sources of livelihood for the community. | Conducted in synergy with district/city governments.                                                                                             | Directed at non-agricultural livelihood sources (off-farm). Local industries that exist need support.                               |
| **2**        | Peatland Stewardship Village is executed in an integrated manner in partnership with HTI companies and palm oil plantations. The goal is to enhance community access.                                                                                                 | Strengthening farmers' livelihoods to protect the remaining peat ecosystems. Formulation of alternative livelihood sources.                      | Livelihood sources oriented towards peat-friendly agriculture, mixed plantations combined with non-agricultural livelihood sources. |
| **3**        | Peatland Stewardship Village is oriented towards fire prevention; conducted in an integrated manner in partnership with HTI companies and palm oil plantations.                                                                                                       | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Livelihoods aimed at forest and land fire prevention. | Livelihood sources oriented towards peat-friendly agriculture and plantations combined with fisheries and livestock.                |
| **4**        | Peatland Stewardship Village geared towards fire prevention; enhancing community access to markets and high-economic value commodities.                                                                                                                               | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
| **5**        | Peatland Stewardship Village focused on fire prevention; enhancing community access to markets and commodities of high economic value.                                                                                                                                | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |

>>>>

::: {style="font-size:20px"}
| Criteria                  | Regional Typologies                                                                                 | Regional Indexes                                                                          |
|---------------------------|-----------------------------------------------------------------------------------------------------|-------------------------------------------------------------------------------------------|
| **What it is**            | Categorises areas based on similar socio-economic, environmental, or institutional characteristics. | A single, composite measure that quantifies the level of vulnerability to a threat.       |
| **Outcome**               | Classifications like "urban area" or "rural area."                                                  | Numerical score ranking areas from low to high vulnerability.                             |
| **Use-case**              | Tailoring policies or interventions to different types of areas.                                    | Prioritising aid, resources, or interventions based on the ranking                        |
| **Caveats**               | Can oversimplify complexities; subject to analyst bias.                                             | May not capture the full situation; choice of indicators and weightings can be arbitrary. |
| **Complementary aspects** | Provides rich, contextual information.                                                              | Pinpoints areas needing immediate attention.                                              |

@@

|-----|-------------------------------|-----------------------------------------------------------|------------------------------------------------------------------------------|

@@

| **Typology** | **R.3.1 Establishment of Peatland Stewardship Village**                                                                                                                                                                                                               | **R.3.2 Enhancing Livelihood Capacity**                                                                                                          | **R.3.3 Development of Alternative Commodities and Livelihood Sources**                                                             |
|--------------|-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------|-------------------------------------------------------------------------------------------------------------------------------------|
| **1**        | \- Community awareness about the importance of the peat ecosystem, collaborating with district and provincial governments. <br><br> - Activities of the Peatland Stewardship Village aimed at increasing income and creating sources of livelihood for the community. | Conducted in synergy with district/city governments.                                                                                             | Directed at non-agricultural livelihood sources (off-farm). Local industries that exist need support.                               |
| **2**        | Peatland Stewardship Village is executed in an integrated manner in partnership with HTI companies and palm oil plantations. The goal is to enhance community access.                                                                                                 | Strengthening farmers' livelihoods to protect the remaining peat ecosystems. Formulation of alternative livelihood sources.                      | Livelihood sources oriented towards peat-friendly agriculture, mixed plantations combined with non-agricultural livelihood sources. |
| **3**        | Peatland Stewardship Village is oriented towards fire prevention; conducted in an integrated manner in partnership with HTI companies and palm oil plantations.                                                                                                       | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Livelihoods aimed at forest and land fire prevention. | Livelihood sources oriented towards peat-friendly agriculture and plantations combined with fisheries and livestock.                |
| **4**        | Peatland Stewardship Village geared towards fire prevention; enhancing community access to markets and high-economic value commodities.                                                                                                                               | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
| **5**        | Peatland Stewardship Village focused on fire prevention; enhancing community access to markets and commodities of high economic value.                                                                                                                                | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
